\huge{A Strategy-Proof Budget Feasible Online Mechanism for Crowdsensing with Time-Discounting Values}

### 2016-11-14 paper.tex
evaluation

However, a well running crowdsensing application needs massive data contributed by the participants to ensure the service quality. Since participating in crowdsensing tasks requires the participants to devote resource consumptions of their smartphones, participants are usually reluctant to share their sensing capabilities(\eg, \cite{Kawajiri:2014:SCI:2632048.2636064,Fan:2015:PTT:2789168.2795179,Karaliopoulos:2016:FLE:2942358.2942369}. Thus, it is necessary to design an incentive mechanism to compensate the participants. According to different settings of scenarios, two cases are often discussed, \ie, offline setting and online setting. Researches on incentive mechanism designs, such as~\cite{yang2012crowdsourcing,koutsopoulos2013optimal}, are usually based on offline scenarios, where participants are present simultaneously while the online scenarios are more common in practice, where participants arrive and leave dynamically. Designing an incentive mechanism in online scenarios is much more complicated, due to the lack of future information. Besides, it brings challenges in the realization of strategy-proofness, since participants may misreport their arrival or departure time in order to gain higher benefits. Here, intuitively, strategy-proofness means that one can maximize her benefit by truthfully revealing her private information (\eg, arrival time, departure time, or sensing cost).

@@

In line 7 in the algorithm 4, the threshold is defined as $\frac{1}{\lambda}\frac{f(\mathbb{D}^{T_k})}{\sum_{i\in\mathbb{D}^{T_k}}b_i}\left(\frac{U}{L}\right)^{l-k}=\frac{1}{\lambda}\frac{f(\mathbb{D}^{T_k})}{B}\frac{B}{\sum_{i\in\mathbb{D}^{T_k}}b_i}\left(\frac{U}{L}\right)^{l-k}\ge\frac{1}{\lambda}\frac{f(\mathbb{D}^{T_k})}{B}\left(\frac{U}{L}\right)$. With the same analysis, it appraoches to $\frac{1}{4}$ as $\omega\to\infty$ and $\lambda\to\frac{U}{4L}$.
\end{proof}
\section{Numerical Results}

In this section, we implement the design of our budget feasible online mechanism with time-discounting values (namely TDM in the simulation). We compare its performance with the optimal offline mechanism (namely OPT) and an online mechanism which randomly selects participants.

In the setup of the evaluation, we first fix some system parameters. The auction period $T$ is set to $50$ and the time slots are divided into $5$ stages. In the large-scale environment~\cite{6979011}, we make a reasonable assumption that the cost of each participant accounts for a tiny part of the total budget. This ratio  is set to $0.0015$ in this paper. The initial threshold at the begin of this auction is set to $0.1$ to avoid possible starvation. The upper bound and lower bound of efficiency are set respectively $2$ and $1$.

@@

\begin{figure}[!t]
  \centering
  \subfigure[Different budgets]{
  \begin{minipage}[b]{0.5\textwidth}
  	\centering
    \includegraphics[width=0.7\textwidth]{BudgetLambda.eps}
    \label{fig:gender_trend}
    \end{minipage}
  }
  \subfigure[Different numbers of participants]{
  \begin{minipage}[b]{0.5\textwidth}
  \centering
    \includegraphics[width=0.7\textwidth]{AgentLambda.eps}
    \label{fig:education_trend}
    \end{minipage}
  }
  \vspace{-0.2cm}
  \caption{Impact of $\lambda\ (\lambda=\lambda_{min}+\frac{\lambda^*}{100}(\lambda_{max}-\lambda_{min}))$.}
  \vspace{-0.2cm}
\end{figure}

In Fig. $3(a)$ and Fig. $3(b)$, we intend to investigate the effect of the system parameter $\lambda$. According to inequality $(9)$, $\lambda$ has an upper bound $\lambda_{max}= \frac{1}{\epsilon}\left(\frac{U}{L}\right)^{l-2}$ and a lower bound $\lambda_{min}=2\left(\frac{U}{L}\right)^{l-1}$, but we don't know how to choose $\lambda$ to maximize the value (even though we can  guarantee a constant competitive ratio). We divide the interval $[\lambda_{min}, \lambda_{max})$ into 100 pieces. We should also consider the effect of different budgets and participants. These two figures show us that with  $\lambda$ getting closer to $\lambda_{min}$, the value is getting higher regardless of the different budgets and participant numbers. This is because when $\lambda$ gets smaller, the threshold gets larger and the total value increases as well. The premise of this phenomenon is the huge number of participants. Considering that there are rare participants competing in this auction, if the threshold is large, some participants will be selected later. The total value will decrease due to the time-discounting property. When there are plentiful participants, the participants with less efficiency will lose and never be selected. In addition, we can also see the competitive ratio in expression $(8)$ has a negative correlation with $\lambda$.
%% The file named.bst is a bibliography style file for BibTeX 0.99c

>>>>

However, a well running crowdsensing application needs massive data contributed by the participants to ensure the service quality~\cite{Wang:2015:CQO:2750858.2807513,Han:2016:PPR:2942358.2942385}. Since participating in crowdsensing tasks requires the participants to devote resource consumptions of their smartphones, participants are usually reluctant to share their sensing capabilities(\eg, \cite{Kawajiri:2014:SCI:2632048.2636064,Fan:2015:PTT:2789168.2795179,Karaliopoulos:2016:FLE:2942358.2942369}. Thus, it is necessary to design an incentive mechanism to compensate the participants. According to different settings of scenarios, two cases are often discussed, \ie, offline setting and online setting. Researches on incentive mechanism designs, such as~\cite{yang2012crowdsourcing,koutsopoulos2013optimal}, are usually based on offline scenarios, where participants are present simultaneously while the online scenarios are more common in practice, where participants arrive and leave dynamically. Designing an incentive mechanism in online scenarios is much more complicated, due to the lack of future information. Besides, it brings challenges in the realization of strategy-proofness, since participants may misreport their arrival or departure time in order to gain higher benefits. Here, intuitively, strategy-proofness means that one can maximize her benefit by truthfully revealing her private information (\eg, arrival time, departure time, or sensing cost).

@@

In line 7 in the algorithm 4, the threshold is defined as $\frac{1}{\lambda}\frac{f(\mathbb{D}^{T_k})}{\sum_{i\in\mathbb{D}^{T_k}}b_i}\left(\frac{U}{L}\right)^{l-k}=\frac{1}{\lambda}\frac{f(\mathbb{D}^{T_k})}{B}\frac{B}{\sum_{i\in\mathbb{D}^{T_k}}b_i}\left(\frac{U}{L}\right)^{l-k}\ge\frac{1}{\lambda}\frac{f(\mathbb{D}^{T_k})}{B}\left(\frac{U}{L}\right)$. With the same analysis, it appraoches to $\frac{1}{4}$ as $\omega\to\infty$ and $\lambda\to\frac{U}{4L}$.
\end{proof}
\section{Numerical Results}
In this section, we show the evaluation results.
\subsection{Methodology}
We implement the design of our budget feasible online mechanism with time-discounting values (namely TDM in the simulation). We compare its performance with the optimal offline mechanism (namely OPT) and an online mechanism which randomly selects participants. The optimal result is computed by solving a binary integer program to determine whether to select a participant. We will evaluate in two metrics:
\begin{itemize}
\item Total Value: Total value is the total contributions of all selected participants. In the TDM mechanism, the total value is the summation of each participant's value. In the TDMS mechanism, the total value is the output of a submodular function with the input of selected participant set. We will measure the total value from some aspects, \eg, the total budget, the number of participants and some system parameters.

\item Select Ratio: The select ratio is the percentage of participants who is selected by the mechanism.

\item Budget Utilization: Budget Utilization is the percentage of the used budget.
\end{itemize}
In the setup of the evaluation, we first fix some system parameters. The auction period $T$ is set to $50$ and the time slots are divided into $5$ stages. In the large-scale environment~\cite{6979011}, we make a reasonable assumption that the cost of each participant accounts for a tiny part of the total budget. This ratio  is set to $0.0015$ in this paper. The initial threshold at the begin of this auction is set to $0.1$ to avoid possible starvation. The upper bound and lower bound of efficiency are set respectively $2$ and $1$.
\subsection{Total Value}
We compare our total value with the OPT and Random algorithm. We change the budget and number of participants respectively.

@@

\begin{figure}[!t]
  \centering
  \subfigure[Different budgets]{
  \begin{minipage}[b]{0.5\textwidth}
  	\centering
    \includegraphics[width=0.7\textwidth]{BudgetLambda.eps}
    \label{fig:gender_trend}
    \end{minipage}
  }
  \subfigure[Different numbers of participants]{
  \begin{minipage}[b]{0.5\textwidth}
  \centering
    \includegraphics[width=0.7\textwidth]{AgentLambda.eps}
    \label{fig:education_trend}
    \end{minipage}
  }
  \vspace{-0.2cm}
  \caption{Impact of $\lambda\ (\lambda=\lambda_{min}+\frac{\lambda^*}{100}(\lambda_{max}-\lambda_{min}))$.}
  \vspace{-0.2cm}
\end{figure}
We then find the effect of the system parameter $\lambda$ on the total value, with different budget and number of participants.

In Fig. $3(a)$ and Fig. $3(b)$, we intend to investigate the effect of the system parameter $\lambda$. According to inequality $(9)$, $\lambda$ has an upper bound $\lambda_{max}= \frac{1}{\epsilon}\left(\frac{U}{L}\right)^{l-2}$ and a lower bound $\lambda_{min}=2\left(\frac{U}{L}\right)^{l-1}$, but we don't know how to choose $\lambda$ to maximize the value (even though we can  guarantee a constant competitive ratio). We divide the interval $[\lambda_{min}, \lambda_{max})$ into 100 pieces. We should also consider the effect of different budgets and participants. These two figures show us that with  $\lambda$ getting closer to $\lambda_{min}$, the value is getting higher regardless of the different budgets and participant numbers. This is because when $\lambda$ gets smaller, the threshold gets larger and the total value increases as well. The premise of this phenomenon is the huge number of participants. Considering that there are rare participants competing in this auction, if the threshold is large, some participants will be selected later. The total value will decrease due to the time-discounting property. When there are plentiful participants, the participants with less efficiency will lose and never be selected. In addition, we can also see the competitive ratio in expression $(8)$ has a negative correlation with $\lambda$.
%% The file named.bst is a bibliography style file for BibTeX 0.99c
\subsection{Select Ratio}
\subsection{Budget Utilization}
